Data Management \\ and LSST Special Programs

### 2018-06-18 DMTN-065.tex
fixed typo

Step 3. Delivery of LSST Processed Images. \\
Pending the issues mentioned above, the raw, reduced, and calibrated exposures and difference images from the Level 1 pipeline are made available within  \texttt{L1PublicT} (currently 24 hours; LSR-REQ-0104).

>>>>

Step 3. Delivery of LSST Processed Images. \\
Pending the issues mentioned above, the raw, reduced, and calibrated exposures and difference images from the Prompt pipeline are made available within  \texttt{L1PublicT} (currently 24 hours; LSR-REQ-0104).
